### 2018-03-31 paper/sexSelectionSpacing-ver1.tex
Edit abstract

Strong son preference is typically associated with shorter birth spacing
in the absence of sons, but access to sex selection has the potential to
reverse this pattern because each abortion extends spacing by six to
twelve months. 
I introduce a statistical method that simultaneously
accounts for how sex selection increases both the likelihood of a son
and the spacing between births. 
Using four rounds of India's National
Family and Health Surveys, I first show that, except for first births,
the spacing between births increased substantially over the last four
decades. 
Birth spacing increased the most for women most likely to use
sex selection; specifically, well-educated women with no boys now
exhibit significantly longer spacing and more male-biased sex ratios
than those with boys. 
Women with no education still follow the standard
pattern of short spacing when they have girls and little evidence of sex
selection, with medium-educated women showing mixed results. 
Finally,
sex ratios are more likely to decline within spells at lower parities,
where there is less pressure to ensure a son, and more likely to
increase or remain consistently high for higher-order spells, where the
pressure to provide a son is high.

>>>>

Strong son preference is typically associated with shorter birth spacing
in the absence of sons, but access to sex selection has the potential to
reverse this pattern because each abortion extends spacing by six to
twelve months. 
I introduce a statistical method that simultaneously
accounts for how sex selection increases the spacing between 
births and the likelihood of a son. 
Using four rounds of India's National
Family and Health Surveys, I show that, except for first births,
the spacing between births increased substantially over the last four
decades, with the most substantial increases among women most 
likely to use sex selection.
Specifically, well-educated women with no boys now
exhibit significantly longer spacing and more male-biased sex ratios
than similar women with boys. 
Women with no education still follow the standard
pattern of short spacing when they have girls and little evidence of sex
selection, with medium-educated women showing mixed results. 
Finally,
sex ratios are more likely to decline within spells at lower parities,
where there is less pressure to ensure a son, and more likely to
increase or remain consistently high for higher-order spells, where the
pressure to provide a son is high.
